---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Rachel Baxter"
date: "8/29/2019"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1
There are 1846 rows and 3 columns. THe variables included to the dataframe are: dataset, x, and y.


### Exercise 2

The answers for this Exercise are given for you below. But you should clean up some of the narrative so that it only includes what you want to turn in.) -- **Answers are after the code chunks.**


First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The plot is in the shape of a *dinosaur*.

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

The correlation coefficient is *-0.0645*.

### Exercise 3

```{r plot-star, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

This plot is in the shape of a *star*.

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))

```

The correlation coefficient is *-0.0629611*.

### Exercise 4
The shape of this plot is an *oval with hat*.

```{r plot-circle, fig.height=3, fig.width=6}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))

```

The correlation coefficient is *-0.06834336*.

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)